Bayesian exponential random graph modeling of KWL Burial network

### 2020-11-22 analysis/paper/paper.Rmd
make density plots for goods for class assignment and model it

<!--posterior stats for pre-E-->
We compared estimated statistics from the posterior distributions to examine their differences in  structure of the simulated networks (Table XX). For the pre-European network simulations, two nodal covariates, age-homophily and ritual-homophily, have significant effects on the relations between burials. The age homophily shows a negative effect that indicates burials of the same age tend to not share similar prestige goods, while the ritual-homophily demonstrates the positive effect that means burials with ritual pottery tend to form relations. Despite positive values for some covariates, such as sex-homophily and burial value-homophily, they do not show a significant tendency to form relations duo to value of zero in the confidence intervals. Similarly, the dyadic covariate, physical distance, shows positive effects but not significantly, indicating that physical proximity does not affect relations. For the endogenous network effects, both transitivity (gwesp) and popularity (gwdegree) present significant positive effects. The positive value for transitivity suggests a tendency of burials to be clustered in closed transitive structures, while positive popularity indicates a tendency toward centralization that means the presence of a limited number of burials with many more relations than others. <!-- what is the social anthropological implication for these values -->

>>>>

<!--posterior stats for pre-E-->
We compared estimated statistics from the posterior distributions to examine their differences in  structure of the simulated networks (Table XX). For the pre-European network simulations, two nodal covariates, age-homophily and ritual-homophily, have significant effects on the relations between burials. The age homophily shows a negative effect that indicates burials of the same age tend to not share similar prestige goods, while the ritual-homophily demonstrates the positive effect that means burials with ritual pottery tend to form relations. Despite positive values for some covariates, such as sex-homophily and burial value-homophily, they do not show a significant tendency to form relations duo to value of zero in the confidence intervals. Similarly, the dyadic covariate, physical distance, shows positive effects but not significantly, indicating that physical proximity does not affect relations. For the endogenous network effects, both transitivity (gwesp) and popularity (gwdegree) present significant positive effects. The positive value for transitivity suggests a tendency of burials to be clustered in closed transitive structures, indicative of the presence of multiple corporate groups sharing burial goods in common. The positive popularity shows a tendency toward centralization that reflects a limited number of burials have many more relations than others. This implies that a few central individuals developed personal networks through wealth accumulation in terms of the flow of goods.
